---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rWinePredictor

<!-- badges: start -->
<!-- badges: end -->

The goal of rWinePredictor is to provide functions that may be useful when building classifiers. This package was originally inteded for a wine quality classifier based on physical and chemical properties of the wine but functions in this package can be used in other models.

## Functions included 

- `generate_summary_stats`: Groups input data by factors of target variable and summarizes counts and means for each class across all parameters in the dataset.

- `create_lineplot`: Creates a line plot with data points (scatter plot + line plot) and has the option to include the axis titles and plot title.

- `calculate_model_metrics`: Calculates a specified model metric (e.g., accuracy, precision, recall) for a given set of predictions and ground truth values.

## Place within the R package ecosystem

`rWinePredictor` is similar to other R packages but does away with long codeblocks and streamlines the process of building classification models. Firstly, `generate_summary_stats` uses `dplyr`’s `group_by` and `summarize` but it calculates the mean of all columns in the set for all facts in the target column. This is an elegant and easy-to-use solution for EDA. Additionally, `create_lineplot` is built using `ggplot2` but also creates line plots in a simple manner, where a user has to just specify the dataset, x and y columns, and whether to include a title or not. Lastly, `calculate_model_metrics` allows users to quickly assess their models; it is built using `parsnip` but allows for an easy solution when users want to benchmark their models quickly.

## Installation

You can install the development version of rWinePredictor from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310-2024/rWinePredictor")
```

## Example

A dataset may look like this: 

```{r}
df <- data.frame(
  quality = c('good', 'bad', 'good'),
  alcohol = c(10, 12, 14),
  sugars = c(1.5, 20, 7.7),
  pH = c(3.3, 4, 2.9),
  stringsAsFactors = TRUE
)
```

We can import this package and begin with some EDA by generating summary data grouped by the classes of the target variable in our dataset using `rWinePredictor::generate_summary_stats()`

```{r}
library(rWinePredictor)

generate_summary_stats(df, quality)
```

When building the model, you will likely tune the hyperparamters. This package has a function for generating scatter plots with connecting lines to find the ideal hyperparamter value. For example you might have a set of accuracies for given k values in a K-NN model. Using `rWinePredictor::create_lineplot()`, you can plot these values.

```{r}
acc_k <- data.frame(
  acc = c(0.6, 0.75, 0.73, 0.7, 0.68, 0.62),
  k_val = c(1, 6, 11, 16, 21, 26))

plt <- create_lineplot(acc_k, k_val, acc)

plot(plt)
```

Lastly, different model metrics can easily be calculated using `rWinePredictor::calculate_model_metric()`.

```{r}
library(yardstick)

model_df = yardstick::two_class_example

accuracy <- calculate_model_metric(model_df, truth_col='truth', predictions_col='predicted', metric="accuracy")

accuracy
```
